TKT RNAseq Experiment: Differential Expression Analysis

### 2023-06-21 TKT_RNAseq/R Code/EdgeR_Analysis.Rmd
fixed metadata table

@@

@@

@@

@@

@@

```{r echo = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}

>>>>

write.csv(all.groups, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")

@@

all.cpmgenes = unique(c(row.names(cpmdata3),row.names(cpmdata4)))

all.cpmdata = matrix(NA, ncol = 33, nrow = length(all.cpmgenes))
colnames(all.cpmdata) = c(colnames(cpmdata3),colnames(cpmdata4))
row.names(all.cpmdata) = all.cpmgenes

all.cpmdata[row.names(cpmdata3),colnames(cpmdata3)] = cpmdata3
all.cpmdata[row.names(cpmdata4),colnames(cpmdata4)] = cpmdata4

all.groups = groups[colnames(all.cpmdata),]

all.TKT.EdgeR = all.cpmdata[, 1:14]
colnames(all.TKT.EdgeR) = c('GRF.CxDf', 'GRF.CxOE', 
                            'WTF.CxDf', 'WTF.CxOE', 
                            'GRxWT.FC', 'GRxWT.FDf', 'GRxWT.FOE',
                            'GRM.CxDf', 'GRM.CxOE', 
                            'WTM.CxDf', 'WTM.CxOE', 
                            'GRxWT.MC', 'GRxWT.MDf', 'GRxWT.MOE')

row.names(all.TKT.EdgeR) = row.names(all.cpmdata)

all.TKT.EdgeR[,1] = GR.F.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,2] = GR.F.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,3] = WTF.CxDf = WT.F.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,4] = WTF.CxOE = WT.F.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,5] = GRxWT.FC = GRxWT.F3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,6] = GRxWT.FDf = GRxWT.FDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,7] = GRxWT.FOE = GRxWT.FOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,8] = GRM.CxDf = GR.M.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,9] = GRM.CxOE = GR.M.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,10] = WTM.CxDf = WT.M.CxDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,11] = WTM.CxOE = WT.M.CxOE3[row.names(all.cpmdata),'FDR']

all.TKT.EdgeR[,12] = GRxWT.MC = GRxWT.M3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,13] = GRxWT.MDf = GRxWT.MDf3[row.names(all.cpmdata),'FDR']
all.TKT.EdgeR[,14] = GRxWT.MOE = GRxWT.MOE3[row.names(all.cpmdata),'FDR']

##write.csv(all.cpmdata, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT_cpmdata.csv")
##write.csv(all.groups, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.metadata.csv")
##write.csv(all.TKT.EdgeR, "/Users/johncsantiago/Documents/GitHub/WhartonLab/TKT_RNAseq/CountTables/TKT.EdgeR.Table.csv")

@@

Female.Only.trim = c(nrow(sGR.F.CxDf3), nrow(sGR.F.CxOE3),
           nrow(sWT.F.CxDf3), nrow(sWT.F.CxOE3),
           nrow(sGRxWT.F3), nrow(sGRxWT.FDf3), nrow(sGRxWT.FOE3))

Male.Only.trim = c(nrow(sGR.M.CxDf3), nrow(sGR.M.CxOE3),
         nrow(sWT.M.CxDf3), nrow(sWT.M.CxOE3),
         nrow(sGRxWT.M3), nrow(sGRxWT.MDf3), nrow(sGRxWT.MOE3))

@@

fig <- fig %>% add_trace(y = ~Female.Only.trim, name = 'Trim Only Female',
                         marker = list(color = c("red"),
                                       line = list(color = "black", width = 1.5)))

@@

fig <- fig %>% add_trace(y = ~Male.Only.trim, name = 'Trim Only Males',
                         marker = list(color = c("blue"),
                                       line = list(color = "black", width = 1.5)))

@@

```{r echo = F, include = F, fig.height=10, fig.cap='Heatmaps of Total DEGs in GR.FC x GR.FDf.'}
